\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-18 paper.tex
Contribution Rachid - HATP

Our execution controllers rely on symbolic task planning to convert long-term
desires into a succession of atomic actions. We use in our architecture the HATP
planner (for Human Aware Task Planner~\cite{Alili2008, Alili2009}).  HATP is a
refinement of a Hierarchical Task Network (HTN). As an HTN, it performs an
iterative task decomposition into sub-tasks until reaching atomic actions. The
\emph{planning domain} defines the set of methods describing how to decompose a
task and represents the procedural knowledge of the robot. It is stored outside
of the central knowledge base, using a specific formalism (see the related
discussion at the end of this section).

@@

The originality of HATP resides in its ability to produce plans for the robot's
actions \emph{as well as} for the other participants (humans or robots), that we
call \emph{shared plans}. This effectively enriches the interaction capabilities
of the robot by allowing for a form of human behaviour \emph{prediction}, which
is used by the robot execution controller to monitor the engagement of the human
partner during joint tasks.

@@

In addition to these costs, HATP also takes into account a set of social rules.
Social rules are heuristics aiming at leading the plan construction towards the
best plan according to some human preferences.  The social rules we have defined
so far deal with \emph{undesirable states} to avoid a state in which the human
could feel uncomfortable; \emph{undesirable sequences} to eliminate sequences of
actions that can be misinterpreted by the human; \emph{effort balancing} to
adjust the work effort of each of the agents; \emph{no wasted time} to avoid
long delays between the actions of the human partner; and \emph{no intricate
links} to limit dependencies between the actions of two or more agents.

>>>>

Our execution controllers rely on symbolic task planning to convert long-term
desires into a succession of atomic actions. We use in our architecture the HATP
planner (for Human Aware Task Planner~\cite{Alili2008,
Alili2009,Lallement2014}).

HATP (Hierarchical Agent- based Task Planner) planning framework extends the
traditional HTN (Hierarchical Task Network) planning domain representation and
semantics by making them more suitable to elaborate plans which involve humans
and robots acting together toward a joint goal. HATP is used by the robot to
elaborate human-robot \emph{shared plans} which are then used to anticipate
human action, to propose to human to act or even to ask help from the human.

The HATP \emph{planning domain} defines a set of methods describing how to
decompose a task and represents the procedural knowledge of the robot as well as
its knowledge about the actions that the human partner is able to achieve. It is
stored outside of the central knowledge base, using a specific formalism (see
the related discussion at the end of this section).

@@

The originality of HATP resides in its ability to produce plans for the robot's
actions \emph{as well as} for the other participants (humans or robots), that we
call \emph{shared plans}.

An important feature of HATP is that it treats agents as ``first-class
entities'' in the domain representation language. It can therefore
distinguish between the different agents in the domain as well as
between agents and the other entities such as tables and chairs. This
facilitates a post-processing step in HATP that splits the final
solution (sequence of actions) into two (or more if there are several
humans) synchronised solution
streams, one for the robot and one for the human, so that the streams may be executed in
parallel and synchronised when necessary.

This effectively enriches the interaction capabilities
of the robot by allowing for a form of human behaviour \emph{prediction}, which
is used by the robot execution controller to monitor the engagement of the human
partner during joint tasks.

@@

To address some of those challenges HATP includes mechanisms called
"social tules" to filter plans so as to keep only those suitable for
HRI. To this end, HATP allows the specification of the following
filtering criteria:

\emph{Wasted time}: Avoids plans where the human mentioned in a plan spends a lot
of its time waiting.

\emph{Effort balancing:} Avoids plans where efforts are
not fairly distributed among the agents mentioned in a plan.  It is
indeed sometimes beneficial to balance efforts between the human and
the robot.

\emph{Control of intricacy:} Avoids plans with too many interdependencies
between the actions of agents mentioned in the plan, as a problem with
executing just one of those actions could invalidate the entire
plan. Also intricate human-robot activity may cause discomfort since
the human will find himself repeatedly in a situation where his is
waiting for the robot to act

\emph{Undesirable sequences:} Avoids plans that violate specific user-defined
sequences (for instance sequences which can be misinterpreted by the human).

Combining some of the above criteria could help yield the
following interesting \emph{shared plans}: (1) the human ends up doing a
number of the tasks, but yet the overall effort is significantly lower than what the robot puts
to do a lower number of effort-intensive tasks; (2) avoiding, when
possible, having the human wait for the robot several times, which
essentially prevents the streams from having too many causal links
between them.

 In the current implementation, the so-called social rules are
implemented by looking through all the plans produced and filtering
out the ones that do not meet the requirements specified. In the
future we intend to study algorithms that do such filtering online,
rather than after primitive solutions are found.
